Co-moving stars in \textsl{Gaia DR1}: a catalog of genuine comoving star pairs from low-resolution spectroscopic follow-up

### 2017-06-05 paper/comoving-followup.tex
words
spacing around cmd

To select candidate pairs for follow-up spectroscopic observations, we only
consider mutually exclusive star pairs within $200~\pc$ in Heliocentric
distance; with the SNR cut used above and given the limitations of the \tgas\
catalog itself, \tgas\ is $\approx$90\% complete to $200~\pc$
(\citealt{Bovy:2017}).
From this source target list, we randomly observed targets with airmass $\sec z
< 1.5$.

\todo{color-magnitude diagram of all stars observed, color our targets
different from the calibration targets}
\figurename~\ref{fig:sample-cmd} shows a color-magnitude diagram of all targets
observed in this observing run (markers) plotted over the density of all \tgas\
stars within $200~\pc$.

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{mcmc_trace.pdf}
  \end{center}
  \caption{%
    \todo{Some summary plots about the MCMC fits...}
    \label{fig:Halpha-mcmc}}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{example_fit.pdf}
  \end{center}
  \caption{%
    \todo{More MCMC bullshit.}
    \label{fig:compare-previous}}
\end{figure}

>>>>

To select candidate pairs for follow-up spectroscopic observations, we only
consider mutually exclusive star pairs within $200~\pc$ in Heliocentric
distance; with the SNR cut used above and given the limitations of the \tgas\
catalog itself, \tgas\ is $\approx$90\% complete to $200~\pc$
(\citealt{Bovy:2017}).
From this source target list, we randomly observed targets with airmass $\sec z
< 1.5$.
\figurename~\ref{fig:sample-cmd} shows a color-magnitude diagram of all targets
observed in this observing run (markers) plotted over the density of all \tgas\
stars within $200~\pc$.

@@

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{mcmc_corner.pdf}
  \end{center}
  \caption{%
    \todo{Some summary plots about the MCMC fits...}
    Small uncertainty in centroid = 2 km/s velocity precision here.
    \label{fig:Halpha-mcmc}}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=\linewidth]{mcmc_example_fit.pdf}
  \end{center}
  \caption{%
    Top shows background linear model + Voigt line model.

    \label{fig:compare-previous}}
\end{figure}
